### 2014-06-05 writing/S'14 paper/join.tex
Few more assorted paper edits.

\begin{table}[htp]
  \centering  
  \setlength{\arraycolsep}{8pt}
  \renewcommand{\arraystretch}{1.1}
  \newcommand{\UNK}{\cdot}  
  $\begin{array}[t]{c@{ \ }|*{7}{c}|}
    %\hline
    \multicolumn{1}{c}{}
             & \nateq     & \natfor     & \natrev     & \natneg    & \natalt     & \natcov     & \multicolumn{1}{c}{\natind} \\
    \cline{2-8}
    \nateq  & \nateq &   \natfor &  \natrev &  \natneg &   \natalt &  \natcov &  \natind \\
    \natfor & \natfor &  \natfor &  \UNK &  \natalt &   \natalt &  \UNK &  \UNK \\
    \natrev & \natrev &  \UNK &  \natrev &  \natcov &   \UNK &  \natcov &  \UNK \\
    \natneg & \natneg &  \natcov &  \natalt &  \nateq &    \natrev &  \natfor &  \natind \\
    \natalt & \natalt &  \UNK &  \natalt &  \natfor &   \UNK &  \natfor &  \UNK \\
    \natcov & \natcov &  \natcov &  \UNK &  \natrev &   \natrev &  \UNK &  \UNK \\
    \natind & \natind & \UNK &  \UNK &  \natind &  \UNK &  \UNK &  \UNK \\
    \cline{2-8}
  \end{array}$
  \caption{Full set of inferences between natural logic relations.
    Given $a \mathbin{R} b$ and $b \mathbin{S} c$, where $R$ and $S$
    are the row and column relations, respectively, and $a$, $b$, and
    $c$ are arbitrary formulae, the table provides the relation
    $a \mathbin{T} c$.}
  \label{tab:jointable}
\end{table}

@@

We found that the RNTN model worked best with 11-dimensional vector representations for the
80 sets and a 90-dimensional feature vector for the classifier. This
model was able to correctly label 99.3\% of the provably derivable test
examples, and 99.1\% of the remaining test examples. The simpler RNN model
worked best with 11 and 75 dimensions, respectively, but was able to
achieve accuracies of only 90.0\% and 87.0\%, respectively.

>>>>

\begin{table}[htp]
  \centering  
  \setlength{\arraycolsep}{8pt}
  \renewcommand{\arraystretch}{1.1}
  \newcommand{\UNK}{\cdot}  
  $\begin{array}[t]{c@{ \ }|*{7}{c}|}
    %\hline
    \multicolumn{1}{c}{}
             & \nateq     & \natfor     & \natrev     & \natneg    & \natalt     & \natcov     & \multicolumn{1}{c}{\natind} \\
    \cline{2-8}
    \nateq  & \nateq &   \natfor &  \natrev &  \natneg &   \natalt &  \natcov &  \natind \\
    \natfor & \natfor &  \natfor &  \UNK &  \natalt &   \natalt &  \UNK &  \UNK \\
    \natrev & \natrev &  \UNK &  \natrev &  \natcov &   \UNK &  \natcov &  \UNK \\
    \natneg & \natneg &  \natcov &  \natalt &  \nateq &    \natrev &  \natfor &  \natind \\
    \natalt & \natalt &  \UNK &  \natalt &  \natfor &   \UNK &  \natfor &  \UNK \\
    \natcov & \natcov &  \natcov &  \UNK &  \natrev &   \natrev &  \UNK &  \UNK \\
    \natind & \natind & \UNK &  \UNK &  \natind &  \UNK &  \UNK &  \UNK \\
    \cline{2-8}
  \end{array}$
  \caption{Inference path from premises $a R S$ (row) and $b S c$ (column) to the relation that holds between $a$ and $c$, if any.  These inferences are based on basic set-theoretic truths about the meanings of the underlying relations as described in Table~\ref{b-table}. We assess our model's ability to reproduce such inferential paths.}
  \label{tab:jointable}
\end{table}

@@

\paragraph{Results.} We found that the RNTN model worked best with 11-dimensional vector representations for the
80 sets and a 90-dimensional feature vector for the classifier. This
model was able to correctly label 99.3\% of the provably derivable test
examples, and 99.1\% of the remaining test examples. The simpler RNN model
worked best with 11 and 75 dimensions, respectively, but was able to
achieve accuracies of only 90.0\% and 87.0\%, respectively.

### 2014-06-05 writing/S'14 paper/quantifiers.tex
Few more assorted paper edits.

\section{Reasoning with natural language quantifiers}\label{sec:quantifiers}

@@

The results for these experiments are shown in Figure \ref{resultstable}. We compare the results to a most frequent class baseline, which reflects the frequency in the test data of most frequent class in the training data, $\natind$.

>>>>

\section{Reasoning with natural language quantifiers and negation}\label{sec:quantifiers}

@@

\paragraph{Results.} The results for these experiments are shown in Figure \ref{resultstable}. We compare the results to a most frequent class baseline, which reflects the frequency in the test data of most frequent class in the training data, $\natind$.

### 2014-06-05 writing/S'14 paper/recursion.tex
Few more assorted paper edits.

\section{Recursive structure}\label{sec:recursion}

@@

We trained both the RNN and RNTN models on the data of size four or
less (65k pairs), and tested it on examples of up to size 12 (44k
pairs). We initialized the model parameters randomly, including the
vector representations of the six variables. The results are shown in
Figure~\ref{prop-results}. In tuning, we found that the RNN model was
approximately optimal with 45-dimensional vector representations, and
the RNTN model was approximately optimal with 25 dimensions. We fixed
the size of the feature vector for the classifier at 75 dimensions. We
found that the RNTN model was able to perform almost perfectly on
unseen small test examples, with accuracy above 99\% below size four.
After depth four, performance gradually falls with increasing size.
The RNN model did not perform well, reaching only 88.2\% accuracy on
the smallest test examples, and declining from there to near-baseline
performance at size 12.

>>>>

\section{Recursive structure in propositional logic}\label{sec:recursion}

@@

\paragraph{Results.} We trained both the RNN and RNTN models on the data of size four or
less (65k pairs), and tested it on examples of up to size 12 (44k
pairs). We initialized the model parameters randomly, including the
vector representations of the six variables. The results are shown in
Figure~\ref{prop-results}. In tuning, we found that the RNN model was
approximately optimal with 45-dimensional vector representations, and
the RNTN model was approximately optimal with 25 dimensions. We fixed
the size of the feature vector for the classifier at 75 dimensions. We
found that the RNTN model was able to perform almost perfectly on
unseen small test examples, with accuracy above 99\% below size four.
After depth four, performance gradually falls with increasing size.
The RNN model did not perform well, reaching only 88.2\% accuracy on
the smallest test examples, and declining from there to near-baseline
performance at size 12.
